A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-30 4_method.tex
rewrite section on marking filtering and initial bead count

@@

\subsubsection{Bead counts}
In order to apply the beading strategy to the ST
we assign each marked node $v$ of the skeleton a bead count $v.B^*$ which is initialized to $b(R(v))$, but it is modified in order to prevent discontinuities and remaining gaps.

We also assign a bead count $v.B^*=b(R(v))$ to all nodes $v$ which are local maxima, i.e. the $v$ for which $\forall v_\text{n} \in v.\text{neighborhood} : R(v) > R(v_\text{n})$. 
This prevents the single overfill or underfill region in unmarked regions.
See \cref{rounded_vs_unrounded}.

@@

>>>>

We mark a node of the skeleton as central if its feature radius is larger than that of all of the neighboring nodes in the skeletal graph.
We also mark whole bones as being central if they are significant according to a common significance measure.

@@

\subsubsection{Marking filtering}
Using the significance measure and the local maximum feature radius condition we initialize all marked bones and nodes.
We then filter out high frequency changes in the marking in order to ensure smooth output toolpaths. 
We perform filtering on the unmarked regions, so that the properties of significant regions mentioned above remain valid.
From each marked node $v_0$ with an upward unmarked bone attached we walk along the upward edges (which cannot branch because of \cref{single_upward_edge}).
If the total length traversed until we reach another marked node $v_1$ is shorter than some filter distance $d_\text{max}^\text{unmarked}$, we mark all bones encountered as being central.

\subsubsection{Bead counts}
In order to apply a beading strategy to the ST we first assign bead counts to the central regions and then decide on how to apply those bead counts outward.
In order to decide on an initial bead count, we require a function mapping a feature diameter to a bead count: $b: \mathbb{R} \to \mathbb{N}$.
(The feature diameter is twice the radius.)
We might choose different functions for $b$ depending on the beading strategy used.

We first assign each marked node $v$ of the skeleton an initial bead count $B^*_v \leftarrow b(2R(v))$, but it is modified in order to prevent high frequency changes in bead count and it is changed in order to account for smooth transitions in bead count.
We also filter unmarked regions where the bead count remains constant.
\todo{Explaining why would have to refer forward to section about interpolating beadings}
From each marked node $v_0$ with an upward unmarked bone attached we walk along the upward edges (which cannot branch because of \cref{single_upward_edge}) until we hit another marked node $v_1$.
If the upper node has the same bead count we mark all bones and nodes $v$ in between, and set the bead count $B^*_{v_0} = B^*_v = B^*_{v_1}$.

\todo{TODO: figure of basic bead counts left, middle with transition mids, right with transition ends.}

@@

\todo{TODO: Replace `distance' with `diameter'.}
